
---
params:
  level: "CHE Region"
  level_value: "Central"
title: "`r paste0(params$level, ': ', params$level_value)`"
subtitle: "Detailed SSP Report"
author: "Alex Axthelm"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
 html_document:
   number_sections: true
   toc: false
   toc_float: true
   code_folding: hide
 pdf_document:
   number_sections: true
   toc: true
---

```{r "knitr setup", include = FALSE, cache = FALSE, eval = TRUE}
knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  message = FALSE,
  warning = TRUE,
  out.width = "100%",
  autodep = TRUE,
  strip.white = TRUE,
  cache.comments = FALSE,
  results = "hold"
  )
```

```{r, Libraries, cache = FALSE, include = FALSE}
library("drake")
library("git2r")
```

**Warning:** This is a draft version, and although I've attempted to ensure
accuracy, the data reported here may not be entirely accurate. If you suspect
that there may be problems, please let me know at
[AAxthelm@che.in.gov](mailto:AAxthelm@che.in.gov), and reference commit
`r git2r::repository() %>% git2r::head() %>% git2r::branch_target() %>% substr(1, 6)`

Data was accurate as of **`r date(file_pull_time)`**

```{r code_for_local_development, include = FALSE, eval = FALSE}
config <- rmarkdown::yaml_front_matter(
  file.path("report.Rmd")
  )
params <- config$params
```

```{r}
loadd(record_data)
loadd(current_senior_cohort)
loadd(dim_ssp)
loadd(period_start)
loadd(dt_extensions)
```

```{r}
student_counts <- record_data %>%
  group_by(hs_grad_year, UQ(as.name(params$level))) %>%
  count()
```

# Time Series

```{r}
timeseries_data <- record_data %>%
  filter(UQ(as.name(params$level)) == params$level_value) %>%
  select(
    hs_grad_year,
    one_of(params$level),
    contains("ssp"),
    contains("all")
    ) %>%
  tidyr::gather(
    key = ssp, value = date,
    -hs_grad_year,
    -UQ(as.name(params$level))
    ) %>%
  filter(!is.na(date)) %>%
  left_join(dim_ssp, by = c("ssp" = "ssp_code")) %>%
  separate(
    col = ssp,
    into = c("name", "number"),
    sep = "_",
    convert = FALSE
    ) %>%
  mutate(
    word_grade = case_when(
      grade == 9 ~ "nine",
      grade == 10 ~ "ten",
      grade == 11 ~ "eleven",
      grade == 12 ~ "twelve",
      1 == 1 ~ "Other"
      ),
    activity_this_year = (current_senior_cohort - hs_grad_year + 12) == grade
    ) %>%
  filter(
    (current_senior_cohort - hs_grad_year + 12) >= grade
    ) %>%
  filter(activity_this_year | name == "all") %>%
  mutate(
    activity = if_else(
      activity_this_year,
      short_name,
      paste(scales::ordinal(grade), "grade Activities")
      )
    ) %>%
  group_by(
    hs_grad_year,
    UQ(as.name(params$level)),
    word_grade,
    activity,
    name,
    date
    ) %>%
  summarise(done_today = n()) %>%
  arrange(date) %>%
  mutate(done_this_year = cumsum(done_today)) %>%
  left_join(student_counts, by = c("hs_grad_year", params$level))
```

```{r}
cumsumplot <- timeseries_data %>%
  # filter(hs_grad_year == 2018) %>%
  filter(date >= period_start) %>%
  filter(name == "all") %>%
  ggplot(
    aes(
      x = date,
      y = done_this_year / n,
      color = word_grade,
      group = activity,
      )
    ) +
  geom_line(size = 1.5) +
  scale_x_date(
    limits = c(period_start, NA),
    date_breaks = "2 months",
    minor_breaks = NULL
    ) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = scales::percent
    ) +
  labs(
    title = "Cumulative SSP completion (All Activites)",
    x = "Date",
    y = "Activities Completed",
    color = "Activity Grade Level"
    ) +
  facet_wrap("hs_grad_year", ncol = 2, labeller = global_labeller) +
  scale_alpha_manual(values = c("ssp" = 1, "all" = 0.6)) +
  scale_color_tfcs() + scale_fill_tfcs() + theme_tfcs()
print(cumsumplot)
```

# School-Level Activity

```{r}
summarise_ssps <- function(data){
  summarise(
    data,
    n = n(),
    ssp_01 = mean(!is.na(ssp_01)),
    ssp_02 = mean(!is.na(ssp_02)),
    ssp_03 = mean(!is.na(ssp_03)),
    ssp_04 = mean(!is.na(ssp_04)),
    ssp_05 = mean(!is.na(ssp_05)),
    ssp_06 = mean(!is.na(ssp_06)),
    ssp_07 = mean(!is.na(ssp_07)),
    ssp_08 = mean(!is.na(ssp_08)),
    ssp_09 = mean(!is.na(ssp_09)),
    ssp_10 = mean(!is.na(ssp_10)),
    ssp_11 = mean(!is.na(ssp_11)),
    ssp_12 = mean(!is.na(ssp_12)),
    FAFSA = mean(!is.na(isir_version)),
    )
}
```

```{r}
summary_table <- record_data %>%
  filter(UQ(as.name(params$level)) == params$level_value) %>%
  # group_by(hs_grad_year, UQ(as.name(params$level))) %>%
  group_by(hs_grad_year, School) %>%
  summarise_ssps() %>%
  mutate_at(vars(starts_with("SSP"), "FAFSA"), funs(scales::percent))
```

## Cohort 2018 Breakdown

```{r}
DT::datatable(
  filter(summary_table, hs_grad_year == 2018),
  extensions = dt_extensions
  )
```

## Cohort 2019 Breakdown

```{r}
DT::datatable(
  filter(summary_table, hs_grad_year == 2019),
  extensions = dt_extensions
  )
```

## Cohort 2020 Breakdown

```{r}
DT::datatable(
  filter(summary_table, hs_grad_year == 2020),
  extensions = dt_extensions
  )
```

## Cohort 2021 Breakdown

```{r}
DT::datatable(
  filter(summary_table, hs_grad_year == 2021),
  extensions = dt_extensions
  )
```
